Dismal Code: Studying the Evolution of Security Bugs

### 2013-04-02 docs/evol.tex
minor changes - fixes

One of the most common approaches to identify security bugs is
{\it static analysis}~\cite{CW07}. This kind of analysis involves the
inspection of the program's source or object code without executing
it. For our research we used {\it FindBugs},\footnote{\url{http://findbugs.sourceforge.net/}}
a static analysis tool that examines bytecode to detect software bugs and has already been used in
research~\cite{AP10}\cite{HP07}\cite{HP04}\cite{HW08}. Specifically, we ran FindBugs on all the project
versions of all the projects that exist in the
{\it Maven Central Repository}\footnote{\url{http://search.maven.org/}}
(approximately 265GB of data). Then we observed the changes that
involved the security bugs and their characteristics. This research builds upon
our earlier work on the topic~\cite{MGS12}.

@@

The main contributions of this research are:
\begin{itemize}
	\item The analysis of how security bugs evolve over time. To achieve
this, we inspect every project per version. Our hypothesis is that security
bugs must decrease as a project evolves since they are critical and developers
should eliminate them.http://search.maven.org/
	\item Security bug persistense between versions. We show evidence that
security bugs are not eliminated between versions.
	\item We show evidence of the relation between security bugs and a project
version's size.  Here, size is defined in terms of bytecode.
	\item The correlation of security bugs with other bug categories. We
show evidence on how such bugs are correlated with bugs that have to do with
performance, coding practices and others.
%	\item The relation of software dependencies and security bugs. Our
%hypothesis is that an artifact that is a dependency of many other artifacts
%should have a low rate of security bugs. 
\end{itemize}

@@

Maven is a build automation tool used primarily for Java projects and it is
hosted by the Apache Software Foundation.\footnote{\url{http://www.apache.org/}}
To describe the software project being built, its dependencies
on other external modules, the build order, and required plug-ins Maven uses
{\sc xml}. To build a software component, it dynamically downloads Java libraries
and Maven plug-ins from the Maven Central Repository,
and stores them in a local cache. The repository can also be updated with new
new projects but also with new versions of existing ones.

@@

\begin{table}
\centering
\caption{Bug Categorisation According to FindBugs}
\label{tbl:bug-cat}
\begin{tabular}{l p{15em}}
\hline
Category & Description\\
\hline
Bad Practice & Violations of recommended and essential
coding practice. \\
Correctness & Involves coding mistakes resulting in code
that was probably not what the developer intended. \\
Experimental & Includes unsatisfied obligations. For instance,
forgetting to close a file. \\
Internationalisation & Indicates the use of non-localized methods. \\
Multi-Threaded Correctness & Thread synchronization issues. \\
Performance & Involves inefficient memory usageallocation, usage 
of non-static classes. \\
Style & Code that is confusing, or
written in a way that leads to errors.\\
Security & Contains two subcategories, namely: {\it Security} and {\it
Malicious Code}. Involves code that could lead to security breach. \\
\hline
\end{tabular}
\end{table}

@@

FindBugs separates software bugs into seven categories (see
Table~\ref{tbl:bug-cat}). Two of them involve security: {\it Security} and {\it
Malicious Code}. From the total number of the {\sc jar}s, 4,353 of them contained
at least one bug coming from the first category
and 45,559 coming from the second.

>>>>

One of the most common approaches to identify security bugs is
{\it static analysis}~\cite{CW07}. This kind of analysis involves the
inspection of the program's source or object code without executing
it. For our research we used {\it FindBugs},\footnote{\url{http://findbugs.sourceforge.net/}}
a static analysis tool that examines bytecode to detect software bugs and has already been used in
research~\cite{AP10}\cite{HP07}\cite{HP04}\cite{HW08}. Specifically, we ran FindBugs on all the project
versions of all the projects that exist in the
{\it Maven Central Repository}\footnote{\url{http://search.maven.org/}}
(approximately 265GB of data - see Section~\ref{sec:data}).
Then we observed the changes that involved the security bugs and their characteristics.
This research builds upon our earlier work on the topic~\cite{MGS12}.

@@

The main contributions of this research are:
\begin{itemize}
	\item The analysis of how security bugs evolve over time. To achieve
this, we inspect every project per version. Our hypothesis is that security
bugs must decrease as a project evolves since they are critical and developers
should eliminate them.
	\item Security bug persistense between versions. We show evidence that
security bugs are not eliminated between versions.
	\item We show evidence of the relation between security bugs and a project
version's size.  Here, size is defined in terms of bytecode.
	\item The correlation of security bugs with other bug categories. We
show evidence on how such bugs are correlated with bugs that have to do with
performance, coding practices and others.
%	\item The relation of software dependencies and security bugs. Our
%hypothesis is that an artifact that is a dependency of many other artifacts
%should have a low rate of security bugs. 
\end{itemize}

@@

Maven is a build automation tool used primarily for Java projects and it is
hosted by the Apache Software Foundation.\footnote{\url{http://www.apache.org/}}
To describe the software project being built, its dependencies
on other external modules, the build order, and required plug-ins Maven uses
{\sc xml}. To build a software component, it dynamically downloads Java libraries
and Maven plug-ins from the Maven central repository,
and stores them in a local cache. The repository can be updated with
new projects and also with new versions of existing projects.

@@

\begin{table}
\centering
\caption{Bug Categorisation According to FindBugs}
\label{tbl:bug-cat}
\begin{tabular}{l p{15em}}
\hline
Category & Description\\
\hline
Bad Practice & Violations of recommended and essential
coding practice. \\
Correctness & Involves coding mistakes resulting in code
that was probably not what the developer intended. \\
Experimental & Includes unsatisfied obligations. For instance,
forgetting to close a file. \\
Internationalisation & Indicates the use of non-localized methods. \\
Multi-Threaded Correctness & Thread synchronization issues. \\
Performance & Involves inefficient memory usageallocation, usage 
of non-static classes. \\
Style & Code that is confusing, or
written in a way that leads to errors.\\
Malicious Code & Involves variables or fields exposed to classes that should
not be using them. \\
Security & Involves input validation issues, unauthorized database connections
and others. \\
\hline
\end{tabular}
\end{table}

@@

FindBugs separates software bugs into nine categories (see
Table~\ref{tbl:bug-cat}). Two of them involve security issues: {\it Security} and {\it
Malicious Code}. From the total number of versions, 4,353 of them contained
at least one bug coming from the first category
and 45,559 coming from the second.
